
\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{booktabs}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
    
\urlstyle{same}

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.8in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}

%-----------------------------------------------------------


\begin{document}

\hspace{0.5cm}\\[-1.8cm]

\textbf{Vamsi Krishna Paluru} \hspace{7.3cm} {\bf linkedin.com/in/Vamsi Krishna Paluru }\\
\indent {\bf paluruvamsikrishna16@gmail.com}  \hspace{8.9 cm} {\bf +91-9985936366 } \\
\indent {\bf }  \hspace{8.0 cm} {\bf } \\

\vspace{-8mm}
\resheading{\textbf{EDUCATION} }\\[\lsep]\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ p{2.5cm} @{\hskip 0.15in} p{5.5cm} @{\hskip 0.15in} p{3.5cm} @{\hskip 0.15in} p{2.5cm} @{\hskip 0.15in} p{1.5cm} }
\toprule
\textbf{Degree} & \textbf{Specialization} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA} \\
\midrule
B.Tech & \textit{Computer Science \& Engineering} & Audisankara & 2024 & 7.48 \\
HSC BIEAP & \textit{Physics, Chemistry, \& Mathematics} & Chaitanya College & 2020 & 9.2\\
SSC  & - & Zpp High School & 2018 & 9.3\\
\bottomrule
\end{tabular}

%\end{center}
%\end{table}
\\ \\

%\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
%\begin{itemize}
%\item \noindent Wireless Network and Network Security, Another one, a third one
%\end{itemize}

\vspace{1mm}

\resheading{\textbf{WORK EXPERIENCE} }

\begin{itemize}

\vspace{-0.5mm}
\item {\bf Web Developer Intern } \textit{[ IIDT - Tirupathi ]}
\textit{\hfill 
{Apr-Jun 2024}
}
\vspace{-1mm}

\begin{itemize}






\item \textbf{Developed} user-friendly interfaces using \textbf{ HTML, CSS,} and \textbf {JavaScript} ensuring a responsive and seamless user experience across devices.

\item \textbf{Collaborated with backend developers } to integrate \textbf{RESTful APIs} and display real-time data, enhancing application functionality.

\item Utilized \textbf{Version control systems (Git)} for collaborative development and efficient project management.

\vspace{-1mm}

\end{itemize}
\end{itemize}

\begin{itemize}

\vspace{-1mm}
\item {\bf Web Developer Intern} \textit{[Slash Mark Startup]}
\textit{\hfill 
{Jan-Apr 2024}
}
\vspace{-1mm}

\begin{itemize}



\item \textbf{Designed } and implemented a responsive and interactive \textbf{E-commerce website} \textbf{using React.js, HTML5 } and \textbf{Tailwind CSS} to ensure a seamless user experience across devices.

\item \textbf{Built core functionalities } including \textbf{user authentication, product catalog, shopping cart,} and \textbf{wishlist features.
}


\item \textbf{Enhanced} website responsiveness and user accessibility using modern design principles

\vspace{-1mm}
\end{itemize}
\end{itemize}


\resheading{\textbf{PROJECTS} }



\begin{itemize}


\item {\bf Portfolio Website} 
\textit{\hfill 
{Jan-Feb 2025}
}



\begin{itemize}

\vspace{-1.5mm}
\item \textbf{Implemented } a dynamic \textbf{E-commerce website} \textbf{"About Me" }section, skill charts, and project showcases with easy navigation.

\item \textbf{Enabled} resume download functionality and embedded links to  \textbf{GitHub, LinkedIn,} and other social platforms in the \textbf{"Follow Me"} section.


\vspace{-1mm}

\end{itemize}
\end{itemize}



\begin{itemize}

 
 
\item {\bf Restaurant Website} 
\textit{\hfill 
{Jul-Aug 2024}
}

\begin{itemize}

\vspace{-1.5mm}

\item \textbf{Designed}nd developed a responsive and interactive restaurant website featuring core sections like  \textbf{Explore Menu, Why Choose Us, Payment section} and  \textbf{Thanking \& Follow Us.} 

\item  \textbf{Delivered} a polished and user-centric website that increased  \textbf{customer engagement} by  \textbf{30\%.} 


\vspace{-2mm}
\end{itemize}
\end{itemize}




\begin{itemize}

 \vspace{-0.5mm}
\item {\bf Meat Delivery Application}
\textit{\hfill 
{Apr-Jun 2024}
}



\begin{itemize}


\vspace{-2mm}
\item \textbf{Developed} user-friendly interfaces using \textbf{ HTML, CSS,} and \textbf {JavaScript} ensuring a responsive and seamless user experience across devices.

\item \textbf{Collaborated with backend developers } to integrate \textbf{RESTful APIs} and display real-time data, enhancing application functionalit

%\item Forecasted the growth in the number of Covid-19 cases over a span of 300+ days across the country through a linear regression model reporting an error of 27.75\% between actual and predicted values


\vspace{-2mm}
\end{itemize}
\end{itemize}

\begin{itemize}


\item {\bf E-Commerce Website
} 
\textit{\hfill 
{Jan-Apr 2024}
}



\begin{itemize}

\vspace{-1.5mm}
\item \textbf{Designed } and implemented a responsive and interactive \textbf{E-commerce website} \textbf{using React.js, HTML5 } and \textbf{Tailwind CSS} to ensure a seamless user experience across devices.

\item \textbf{Built core functionalities } including \textbf{user authentication, product catalog, shopping cart,} and \textbf{wishlist features.
}


\vspace{-1mm}

\end{itemize}
\end{itemize}







\resheading{\textbf{TECHNICAL SKILLS} }
\begin{itemize}
\vspace{-1mm}

\item \textbf{Languages:} Java(Beginner), HTML5, CSS3,Bootstrap, Javascript,React.js and SQl.

\vspace{-1mm}
\item \textbf{Tools: } VS Code.
\vspace{-1mm}

\item \textbf{Version control: } Git and GitHub.
\vspace{-1mm}



\end{itemize}


\end{document}


